TBD

### 2021-02-25 outputs/paper/paper.Rmd
Edit captions of figures

```{r Q3, echo = FALSE, message = FALSE}
### What best describes your restaurant segmentation?
### Fast-food/quick service
### Casual Dining
### Fine Dining
### Other
ggplot(data = all_simulated_dataset, mapping = aes (x = Q3, fill = type)) +
  geom_bar() +
  scale_x_discrete(limit = c ("Fine Dining", "Casual Dining", "Fast-food/quick service", "Other")) +
  labs(x = "Restaurant Type",
       y = "# of Restaurants",
       fill = "Condition",
       title = "Type of restaurant") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

```{r Q4, echo = FALSE, message = FALSE}
### How many years has your restaurant been in operation?
### 1-4 years
### 5-7 years
### 8-10 years
### 10 or more years
ggplot(data = all_simulated_dataset, mapping = aes (x = Q4, fill = type)) +
  geom_bar() + coord_flip() +
  scale_x_discrete(limit = c ("1-4 years", "5-7 years", "8-10 years", "10 or more years")) +
  labs(x = "Years of Operation",
       y = "# of Restaurants",
       fill = "Condition",
       title = str_wrap("Number of years restaurants have been in operation", 30)) +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

```{r Q11, echo = FALSE, message = FALSE}
### Between Oct 1 and Dec 31, which food courier service did you receive the most orders from?
### UberEats
### SkiptheDishes 
### DoorDash
### Other
### In-house delivery service
### None
ggplot(data = all_simulated_dataset, mapping = aes(x = Q11, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("UberEats", "SkiptheDishes", "DoorDash", "In-house delivery service", "Other", "None")) +
  labs(x = "Delivery Service",
       y = "# of Restaurants",
       title = "Food courier service popularity (most orders)",
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) + 
  theme_fivethirtyeight()
```

@@

```{r Q5 + Q6 Table, echo = FALSE, message = FALSE}
### Prior to (intervention start date), how many people did you employ?
### How many people do you currently employ?
t1 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(prior_employees = mean(Q5, na.rm = TRUE, .groups = NULL))
t2 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(curr_employees = mean(Q6, na.rm = TRUE), .groups = NULL)
total <- merge(t1, t2, by = c("type"))
kable(total,
      booktabs = T,
      digits = 3,
      col.names = c("Intervention Group",
                  "# of Employees Prior to Intervention",
                  "Current # of Employees")) %>%
      footnote(general = "Change in # of employees before and after intervention period (Q5 + Q6)") %>%
  kable_paper(c("striped", "hover"))
### T-Tests (Welch's)
#Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
t3 <- t.test(control_q5, treatment_q5, paired = FALSE)
#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
t4 <- t.test(control_q6, treatment_q6, paired = FALSE)

@@

# Output data table
t_tests %>%
  kable(
    booktabs = T,
    digits = 3,
    col.names = c("Mean Difference",
                  "Mean (Pre-Intervention)",
                  "Mean (Post-Intervention)",
                  "t",
                  "p",
                  "df")

@@

```{r Q10, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention), did you make any adjustments to your menu prices?
### Yes, prices were raised
### Yes, prices were lowered
### No changes were made
ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = str_wrap("Menu adjustments between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

>>>>

```{r Q3, echo = FALSE, message = FALSE, fig.cap = "Types of Restaurants"}
### What best describes your restaurant segmentation?
### Fast-food/quick service
### Casual Dining
### Fine Dining
### Other
ggplot(data = all_simulated_dataset, mapping = aes (x = Q3, fill = type)) +
  geom_bar() +
  scale_x_discrete(limit = c ("Fine Dining", "Casual Dining", "Fast-food/quick service", "Other")) +
  labs(x = "Restaurant Type",
       y = "# of Restaurants",
       fill = "Condition",
       title = "Type of restaurant") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

```{r Q4, echo = FALSE, message = FALSE, fig.cap = "Number of years restaurants have been in operation"}
### How many years has your restaurant been in operation?
### 1-4 years
### 5-7 years
### 8-10 years
### 10 or more years
ggplot(data = all_simulated_dataset, mapping = aes (x = Q4, fill = type)) +
  geom_bar() + coord_flip() +
  scale_x_discrete(limit = c ("3 years or less", "5-7 years", "8-10 years", "10 or more years")) +
  labs(x = "Years of Operation",
       y = "# of Restaurants",
       fill = "Condition",
       title = str_wrap("Number of years in operation", 30)) +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

```{r Q10, echo = FALSE, message = FALSE, fig.cap = "The most used food courier service"}
### Between Oct 1 and Dec 31, which food courier service did you receive the most orders from?
### UberEats
### SkiptheDishes 
### DoorDash
### Other
### In-house delivery service
### None
ggplot(data = all_simulated_dataset, mapping = aes(x = Q11, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("UberEats", "SkiptheDishes", "DoorDash", "In-house delivery service", "Other", "None")) +
  labs(x = "Delivery Service",
       y = "# of Restaurants",
       title = "Food courier service popularity",
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) + 
  theme_fivethirtyeight()
```

@@

```{r Q5Q6mean, echo = FALSE, message = FALSE}
### Prior to (intervention start date), how many people did you employ?
### How many people do you currently employ?
t1 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(prior_employees = mean(Q5, na.rm = TRUE, .groups = NULL))
t2 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(curr_employees = mean(Q6, na.rm = TRUE), .groups = NULL)
total <- merge(t1, t2, by = c("type"))
# kable(total,
#       booktabs = T,
#       digits = 3,
#       col.names = c("Group Type",
#                   "# of Employees Prior to Intervention",
#                   "Current # of Employees")) %>%
#       footnote(general = "Change in # of employees before and after intervention period (Q5 + Q6)") %>%
#   kable_paper()
  # This table could be excluded because the means will be displayed anyway in the following T-test table?
```

```{r Q5Q6tTest, echo = FALSE, message = FALSE}
### T-Tests (Welch's)
#Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
t3 <- t.test(control_q5, treatment_q5, paired = FALSE)
#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
t4 <- t.test(control_q6, treatment_q6, paired = FALSE)

@@

# Output data table
t_tests %>%
  kable(
    booktabs = T,
    caption = "Welch's T-test to examine effects of intervention on the number of employees",
    digits = 3,
    col.names = c("Mean Difference",
                  "Mean (Pre-Intervention)",
                  "Mean (Post-Intervention)",
                  "t",
                  "p",
                  "df")

@@

```{r Q11, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention), did you make any adjustments to your menu prices?
### Yes, prices were raised
### Yes, prices were lowered
### No changes were made
ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = str_wrap("Menu adjustments between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
